---
output: pdf_document
Author: Roberto Gutierrez
---
Statistical Inference Project - Part 2  
========================================  

  

###1. Data Summary  



**Description**  

The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid). 

**Format**  

A data frame with 60 observations on 3 variables.
[,1]         len 	numeric 	Tooth length
[,2] 	supp 	factor 	Supplement type (VC or OJ).
[,3] 	dose 	numeric 	Dose in milligrams.

**Source**  

C. I. Bliss (1952) The Statistics of Bioassay. Academic Press.

**References**

McNeil, D. R. (1977) Interactive Data Analysis. New York: Wiley.

 
 
###2. Exploration Analysis  


```{r ,fig.height=16, fig.width=8 , message=FALSE,warning=FALSE}

library(datasets)
library(ggplot2)

data(ToothGrowth)
head(ToothGrowth)

```

As the graph shows the result for the same dose are correlated. It is normal to expect that different subjects under the same dose and treatment would experience similar effects. In order to obtain the right results we compare both "supplements" "pairing" the results by the dose.

```{r}

ggplot(ToothGrowth, aes(x = supp, y = len, colour = factor(dose) ,group = factor(dose))) +
        geom_point(size =5,  alpha = .5) +
        geom_line(size = 1) +
        labs(colour='mg', x='supplement', y='Tooth length') +
        ggtitle("ToothGrowth data: length vs dose, given type of supplement
                ") 

        
```


###3. Confidance Interval  

Paired observations are often analyzed using the $t$ interval by taking differences. In R the $t.test$ function performs one and two sample t-tests on vectors of data. I use this function with the option $paired=TRUE$ for the reason explained previously.

```{r}

t.test(len ~ I(relevel(supp, 2)), paired = TRUE, data = ToothGrowth)

```


###4. Conclusions  

The t-statistic is $t = -3.3026$ and the 95 percent confidence interval: $-5.991341 -1.408659$. Becuase the t-stistic is within the confidance interval, this indicates that with a 95 percent confidance, both supplements have the same effect in the teeth growth.